Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
Dataset
Timeline

@@

\section{Approximate Timeline}
Maybe just a paragraph here

>>>>

\paragraph{Dataset}
We plan to use the ScienceQA dataset. ScienceQA is a multimodal dataset containing science questions and their answers.

@@

\section{Approximate Timeline}
-Now - mid November: 
  Preliminary baseline tests: small LLM relying only on commonsense reasoning / only on pretraining 
  zero-shot, few-shot
  optional: stronger baseline – same LLM with better prompting techniques like CoT/Self-Ask
-mid November - mid December:
  Construct agentic / RAG pipeline with “big smart” model + additional resources.
  optional: soft-prompting for better workflow^ to distill from
-mid December - mid January:
  Knowledge distillation experiments.
